Ion pairing controls rheological properties of ``processionary'' polyelectrolyte hydrogels

### 2016-07-11 PALSE/talk_Kyoto.tex
start Counterion condensation

>>>>

\begin{frame}{Linear rheology}
	\begin{columns}
	\column{0.5\textwidth}
	\tikzsetnextfilename{linear_rheology_PImBr}%
	\input{fig_presentation/linear_rheology_PImBr.pgf}
	\[ G = \frac{c}{N}k_\mathrm{B}T \]
	\begin{description}[$N$]
	\item[$c$] monomer concentration
	\item[$N$] \# monomers between CL
	\end{description}
	\column{0.45\textwidth}
	\pause
	\begin{itemize}
	\item $N \approx 800 N_0$ !
	\item 800 chains between CL
	\end{itemize}
	\begin{flushright}\includegraphics[height=14\baselineskip]{presentation/Thaumetopea_pityocampa_01.jpg}\\
	\vspace{-1.5em}\colorbox{lightgray}{\scriptsize Wikimedia commons}
	\end{flushright}
	\end{columns}
\end{frame}

\begin{frame}{Tweak repeated ions + counterions}
	\vspace{1.5\baselineskip}
	\tikzsetnextfilename{postfunc}%
	\input{fig_presentation/postfunc.pgf}

	\bigskip
	\tikzsetnextfilename{postfunc_chem}%
	\input{fig_presentation/postfunc_chem.pgf}
\end{frame}

\begin{frame}\frametitle{Counterion condensation}
\begin{itemize}
\item Direct Hoffmeister series $\ce{I-}<\ce{Br-}<\ce{Cl-}<\ce{F-}$
\item \ce{\pi+-\pi+} interactions {\tiny\setatomsep{1.5em}$\raisebox{-0.5em}{\chemfig{[2]*5(--N(-)---)}}>\raisebox{-0.5em}{\chemfig{[2]*5(-N(-)-=N-=)}}$}
\end{itemize}
\begin{tikzpicture}
\pgfdeclarelayer{background}
\pgfdeclarelayer{foreground}
\pgfsetlayers{background,main,foreground}
\node at (0.33\columnwidth, -8\baselineskip) {PBr} [->, level distance=5em] 
	child [grow=east] {node(PImBr) {\ce{PIm+Br-}} [level distance=5em]
		child[grow=-45] {node(PImF) {\ce{PIm+F-}}} 
		child {node(PImCl) {\ce{PIm+Cl-}}} 
		child[grow=45] {node(PImI) {\ce{PIm+I-}}}} 
	child [grow=west] {node(PPyrBr) {\ce{PPyr+Br-}} [level distance=5em]
		child[grow=-135] {node(PPyrF) {\ce{PPyr+F-}}} 
		child {node(PPyrCl) {\ce{PPyr+Cl-}}} 
		child[grow=135] {node(PPyrI) {\ce{PPyr+I-}}}};
\begin{pgfonlayer}{background}
	\draw[ilmorange, line width=0.3em, ->] (PImI) to[bend right] (PImBr.north) ..controls (PImBr.center) and (PImCl.center) .. (PImCl.base) to[bend left] (PImF);
	\draw[ilmorange, line width=0.3em, ->] (PPyrI) to[bend left] (PPyrBr.north) ..controls (PPyrBr.center) and (PPyrCl.center) .. (PPyrCl.base) to[bend right] (PPyrF);
\end{pgfonlayer}
	\foreach \x in {PImF,PImCl,PPyrF}{
	\draw[ilmcolor] (\x.north west) -- (\x.base east) (\x.north east) -- (\x.base west) ;
	}
\end{tikzpicture}
